On the Synchronization of Computational RFIDs

### 2018-05-17 TMC-appendix.tex
latest changes

\newpage\null\thispagestyle{empty}\newpage
\appendices
\section{Analysis of Algorithm~\ref{alg:sync}}

We provide the synchronization conditions of Algorithm~\ref{alg:sync} and show that the synchronization will be established eventually. We need to mention that we follow similar calculation steps to the ones presented in the studies~\cite{pi2015,Yildirim:Gradient:2016}. However, since we use a different clock drift model in this article, i.e. Brownian motion rather than uniform distribution, the following  mathematical analysis is moderately different and more realistic as compared to those in the previous studies.

@@

Consider \eqref{eq:gamma_t_1} and without loss of 

@@

indicated in Section \ref{subsec:event_period_uncertainty}). For ease of 

@@

Using \eqref{eq:gamma_t_1}, \eqref{eq:drift_relation} and 

@@

&\overset{\eqref{eq:update_rule},\eqref{eq:drift}}{=}& 

@@

the asymptotic estimation error of Algorithm \ref{alg:sync} is given by

@@

which results in \eqref{eq:sync_performance}.

>>>>

\documentclass[10pt,journal,compsoc]{IEEEtran}

\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  \usepackage[nocompress]{cite}
\else
  % normal IEEE
  \usepackage{cite}
\fi

\usepackage{array}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{stmaryrd}

\newcommand{\expected}[1]{E\!\left\llbracket #1 \right\rrbracket}

\addtocounter{equation}{7}

\begin{document}

\title{On the Synchronization of Computational RFIDs}

\author{Kas{\i}m~Sinan~Y{\i}ld{\i}r{\i}m, 
	Henko~Aantjes, 
	Przemys{\l}a~Pawe{\l}czak~\IEEEmembership{Member,~IEEE,} 
	and~Amjad~Yousef~Majid
	%
	\IEEEcompsocitemizethanks{
		%\IEEEcompsocthanksitem A preliminary version of this article was presented at the HLPC 2016 Workshop, Atlanta, GA, USA, April 2, 2016~\cite{hlpc2016}. \protect\\
		\IEEEcompsocthanksitem The authors are with the Embedded Software Group, Delft University of Technology, Mekelweg 4, 2628 CD Delft, The Netherlands (e-mail: \{k.s.yildirim, p.pawelczak, a.y.majid\}@tudelft.nl, h.aantjes@student.tudelft.nl).
	}
%	\thanks{Manuscript received April 19, 2005; revised August 26, 2015.}
}

\maketitle

\IEEEdisplaynontitleabstractindextext

\IEEEpeerreviewmaketitle

\appendices
\section{Analysis of Algorithm 1}

We provide the synchronization conditions of Algorithm 1 and show that the synchronization will be established eventually. We need to mention that we follow similar calculation steps to the ones presented in the studies~\cite{pi2015,Yildirim:Gradient:2016}. However, since we use a different clock drift model in this article, i.e. Brownian motion rather than uniform distribution, the following  mathematical analysis is moderately different and more realistic as compared to those in the previous studies.

@@

Consider (5) and without loss of 

@@

indicated in Section 6.1). For ease of 

@@

Using (5), \eqref{eq:drift_relation} and 

@@

&\overset{(6),\eqref{eq:drift}}{=}& 

@@

the asymptotic estimation error of Algorithm 1 is given by

@@

which results in (7).

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,references}

\end{document}
